Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-10-26 ms.tex
notes

%We assume the stellar flux $F_s(\lambda)$ is a $6110\,\mathrm{K}$ blackbody \citep{gillon14}.  (FIXME - use a PHOENIX model instead). 
We scaled the planet-to-star flux by a correction factor $c$ to account for dilution from the companion star and ellipsoidal variability due to the planet's tidal distortion. The correction factor took the form: 
\begin{equation}
	c(\lambda, t) = (1 + \alpha(\lambda))A(t)
\end{equation}
where $\alpha(\lambda)$ is the additional fractional flux from the companion star and $A(t)$ is the sky-projected area of the planet. We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier16}. The companion star contributes FIXME percent of the flux at FIXME $\mu$m.  We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid. We assume a Love number $\kappa_n = 0.653$ based on Table B.5 of \cite{leconte11a}, for a highly irradiated, $1.5 R_\mathrm{J}$ planet aged 5 Gyr. The predicted ellipsoidal variability is shown in Figure\,\ref{fig:ellipsoidal}. At quadrature, the project radius is $8\%$ larger than at phase zero (mid-transit). %FIXME: say this doesn't matter.
%In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}. In the observed light curve, changes in planet radius are degenerate with changes in temperature.

>>>>

%We assume the stellar flux $F_s(\lambda)$ is a $6110\,\mathrm{K}$ blackbody \citep{gillon14}.  (FIXME - use a PHOENIX model instead). 
We scaled the planet-to-star flux by a correction factor $c$ to account for dilution from the companion star and ellipsoidal variability due to the planet's tidal distortion. The correction factor took the form: 
\begin{equation}
	c(\lambda, t) = (1 + \alpha(\lambda))A(t)
\end{equation}
where $\alpha(\lambda)$ is the additional fractional flux from the companion star and $A(t)$ is the sky-projected area of the planet. We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier16}. The companion star contributes FIXME percent of the flux at FIXME $\mu$m.  We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid. We estimated the ellipsoid properties using Table B.3 of \cite{leconte11a}, assuming the planet radius is 1.5 $R_\mathrm{Jup}$ and age is 5 Gyr. The predicted ellipsoidal variability is shown in Figure\,\ref{fig:ellipsoidal}. At quadrature, the projected radius is $8\%$ larger than at phase zero (mid-transit). %FIXME: say this doesn't matter.
%In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}. In the observed light curve, changes in planet radius are degenerate with changes in temperature.
